Spatial Coordination Of Stomatal Patterning Between Leaf Surfaces In Amphistomatous \emph{Arabidopsis thaliana} Incurs No Photosynthetic Advantage

### 2023-10-16 ms/ms.tex
updated caption in fig:density and removed extra model description from ms

% Pandoc syntax highlighting
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}

@@

% From pandoc table feature
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}

@@

\usepackage[nomarkers,tablesfirst]{endfloat}
\usepackage{lineno}
\linenumbers
\usepackage{hyperref}
\renewcommand{\figureautorefname}{Fig.}

@@

We modeled photosynthesis CO\(_2\) assimilation rate using a
spatially-explicit two-dimensional reaction diffusion model using a
porous medium approximation
(\protect\hyperlink{ref-parkhurst_intercellular_1994}{\textbf{parkhurst\_intercellular\_1994?}})
using the finite element method (FEM) following
(\protect\hyperlink{ref-earles_excess_2017}{\textbf{earles\_excess\_2017?}}).
Consider a two-dimensional leaf where stomata occur on each surface in a
regular sequence with interstomatal distance \(U\). The main outcome we
assessed is the advantage of offsetting the position of stomata on each
surface compared to have stomata on the same \(x\) position on each
surface. With these assumptions, by symmetry, we only need to model two
stomata, one abaxial and one adaxial, from \(x = 0\) to \(x = U/2\) and
from the adaxial surface at \(y = 0\) to the abaxial surface at
\(y = L\), the leaf thickness. We arbitrarily set the adaxial stomate at
\(x = 0\) and toggled the abaxial stomata position between \(x = U/2\)
(offset) or \(x = 0\) (below adaxial stomate). The `coordination
advantage' of offsett stomatal position on each surface is the
photosynthetic rate of the leaf with offset stomata compared to that
with stomata aligned in the same \(x\) position:

@@

WORKING HERE - ???

\hypertarget{light-propogation-model}{%
\subsubsection{Light propogation model}\label{light-propogation-model}}

Irradiance at depth \(y\) in a leaf with thickness \(L\) is modeled
following Lloyd \emph{et al.} (1992):

\begin{equation}\label{eq:light_propogation}
  I(y) = 1.1 I_0 e ^ {-2.4 y / L}
\end{equation}

where \(I_0\) is photosynthetically active irradiance incident on the
adaxial leaf surface.

\hypertarget{biochemical-model}{%
\subsubsection{Biochemical model}\label{biochemical-model}}

All parameter symbols, units, descriptions, and values are described in
Table X below. Following Gutschick (1984), we modeled photosynthetic
rate per unit chlorophyll \(A_\text{chl}\) then calculated the
volumetric photosynthetic rate \(A_\text{volume}\) by multiplying by the
chlorophyll concentration \(Q_\text{chl}\):

\[A_\text{volume} = A_\text{chl} Q_\text{chl}\] A description of the
model is given on page 553-556 of Gutschick (1984). The R code below is
how we implemented the model.

\begin{itemize}
\tightlist
\item
  \texttt{C\_m} is a vector CO\(_2\) concentrations in
  \(\text{mmol m}^{-3}\) at different positions within the leaf
\item
  \texttt{I\_m} is a vector of irradiances in
  \(\mu \text{mol m}^{-2} \text{s}^{-1}\) at different positions within
  the leaf (same order as \texttt{C\_m}).
\item
  \texttt{pars} is a list of parameters
\end{itemize}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{pars }\OtherTok{=} \FunctionTok{list}\NormalTok{(}

    \AttributeTok{P =} \FunctionTok{set\_units}\NormalTok{(}\FloatTok{101.325}\NormalTok{, kPa), }\CommentTok{\# air pressure at sea level}
    \AttributeTok{temp =} \FunctionTok{set\_units}\NormalTok{(}\FloatTok{298.15}\NormalTok{, K), }\CommentTok{\# assume constant temperature}
    \AttributeTok{R\_gas =} \FunctionTok{set\_units}\NormalTok{(}\FloatTok{8.314}\NormalTok{, J}\SpecialCharTok{/}\NormalTok{K}\SpecialCharTok{/}\NormalTok{mol), }\CommentTok{\# ideal gas constant}

    \CommentTok{\# Calculations for C\_a and O ued below}
    \CommentTok{\# 21\% O2}
    \CommentTok{\# set\_units(0.21 * P / (R\_gas * temp), mol/m\^{}3)}
    \CommentTok{\# 415 ppm}
    \CommentTok{\# set\_units((415/1e6) * P / (R\_gas * temp), mmol/m\^{}3)}

    \CommentTok{\# Environmental}
    \AttributeTok{C\_a =} \FunctionTok{set\_units}\NormalTok{(}\FloatTok{16.96367}\NormalTok{, mmol}\SpecialCharTok{/}\NormalTok{m}\SpecialCharTok{\^{}}\DecValTok{3}\NormalTok{),}
    \AttributeTok{O =} \FunctionTok{set\_units}\NormalTok{(}\FloatTok{8.584027}\NormalTok{, mol}\SpecialCharTok{/}\NormalTok{m}\SpecialCharTok{\^{}}\DecValTok{3}\NormalTok{),}
    \AttributeTok{PAR =} \FunctionTok{set\_units}\NormalTok{(}\DecValTok{1000}\NormalTok{, umol}\SpecialCharTok{/}\NormalTok{m}\SpecialCharTok{\^{}}\DecValTok{2}\SpecialCharTok{/}\NormalTok{s),}

    \CommentTok{\# Biochemical}
    \AttributeTok{E\_t =} \FunctionTok{set\_units}\NormalTok{(}\FloatTok{0.01}\NormalTok{, mol}\SpecialCharTok{/}\NormalTok{mol),}
    \AttributeTok{eta\_t =} \FunctionTok{set\_units}\NormalTok{(}\FloatTok{0.59}\NormalTok{, }\DecValTok{1}\NormalTok{),}
    \AttributeTok{k\_c =} \FunctionTok{set\_units}\NormalTok{(}\DecValTok{20}\NormalTok{, mol}\SpecialCharTok{/}\NormalTok{mol}\SpecialCharTok{/}\NormalTok{s),}
    \AttributeTok{k\_o =} \FunctionTok{set\_units}\NormalTok{(}\FloatTok{4.2}\NormalTok{, mol}\SpecialCharTok{/}\NormalTok{mol}\SpecialCharTok{/}\NormalTok{s),}
    \AttributeTok{K\_c =} \FunctionTok{set\_units}\NormalTok{(}\FloatTok{0.0184}\NormalTok{, mol}\SpecialCharTok{/}\NormalTok{m}\SpecialCharTok{\^{}}\DecValTok{3}\NormalTok{),}
    \AttributeTok{K\_o =} \FunctionTok{set\_units}\NormalTok{(}\FloatTok{13.2}\NormalTok{, mol}\SpecialCharTok{/}\NormalTok{m}\SpecialCharTok{\^{}}\DecValTok{3}\NormalTok{),}
    \AttributeTok{Q\_chl =} \FunctionTok{set\_units}\NormalTok{(}\FloatTok{3.3}\NormalTok{, mol}\SpecialCharTok{/}\NormalTok{m}\SpecialCharTok{\^{}}\DecValTok{3}\NormalTok{),}
    \AttributeTok{R\_p =} \FunctionTok{set\_units}\NormalTok{(}\FloatTok{0.273}\NormalTok{, mol}\SpecialCharTok{/}\NormalTok{mol),}

    \CommentTok{\# Diffusivity of CO2 in leaf airspace. From Gutschick 1984. Should be updated and include temperature dependence, effect of cell packing, tortuosity, etc.}
    \AttributeTok{D\_mc =} \FunctionTok{set\_units}\NormalTok{(}\FloatTok{7e{-}7}\NormalTok{, m}\SpecialCharTok{\^{}}\DecValTok{2}\SpecialCharTok{/}\NormalTok{s)}

\NormalTok{)}

\CommentTok{\# strip units to speed up calculation}
\NormalTok{upars }\OtherTok{=}\NormalTok{ purrr}\SpecialCharTok{::}\FunctionTok{map}\NormalTok{(pars, }\SpecialCharTok{\textasciitilde{}}\NormalTok{ \{}\ControlFlowTok{if}\NormalTok{(}\FunctionTok{inherits}\NormalTok{(.x, }\StringTok{"units"}\NormalTok{)) \{}\FunctionTok{drop\_units}\NormalTok{(.x)\}\})}

\CommentTok{\# multiply/divide by 1e3 because C\_m is mmol and parameters are in mol}
\NormalTok{k\_vc }\OtherTok{=}\NormalTok{ upars[[}\StringTok{"k\_c"}\NormalTok{]] }\SpecialCharTok{/}\NormalTok{ (}\DecValTok{1} \SpecialCharTok{+}\NormalTok{ (}\FloatTok{1e3} \SpecialCharTok{*}\NormalTok{ upars[[}\StringTok{"K\_c"}\NormalTok{]] }\SpecialCharTok{/}\NormalTok{ C\_m) }\SpecialCharTok{*}
\NormalTok{                           (}\DecValTok{1} \SpecialCharTok{+}\NormalTok{ upars[[}\StringTok{"O"}\NormalTok{]] }\SpecialCharTok{/}\NormalTok{ upars[[}\StringTok{"K\_o"}\NormalTok{]])) }\CommentTok{\# [1/s]}
\CommentTok{\# Given light\_propagation assumptions, k = 2.4/L assuming no scattering}
\NormalTok{k\_i }\OtherTok{=} \FloatTok{2.4} \SpecialCharTok{/}\NormalTok{ upars[[}\StringTok{"leaf\_thickness"}\NormalTok{]] }\CommentTok{\# [1/um] \# I\textquotesingle{}m not sure sure this is right}
\NormalTok{b\_x }\OtherTok{=}\NormalTok{ k\_i }\SpecialCharTok{*}\NormalTok{ I\_m }\CommentTok{\# [mol/m\^{}3/s]}
\NormalTok{a\_x }\OtherTok{=}\NormalTok{ b\_x }\SpecialCharTok{/}\NormalTok{ upars[[}\StringTok{"Q\_chl"}\NormalTok{]] }\CommentTok{\# [1/s]}
\NormalTok{j }\OtherTok{=} \FloatTok{0.5} \SpecialCharTok{*}\NormalTok{ a\_x }\SpecialCharTok{*}\NormalTok{ upars[[}\StringTok{"eta\_t"}\NormalTok{]] }\CommentTok{\# [1/s] \# eqn 9}
\NormalTok{phi }\OtherTok{=}\NormalTok{ upars[[}\StringTok{"k\_o"}\NormalTok{]] }\SpecialCharTok{/}\NormalTok{ upars[[}\StringTok{"k\_c"}\NormalTok{]] }\SpecialCharTok{*}\NormalTok{ (upars[[}\StringTok{"O"}\NormalTok{]] }\SpecialCharTok{/}\NormalTok{ upars[[}\StringTok{"K\_o"}\NormalTok{]]) }\SpecialCharTok{/}
\NormalTok{  (}\FloatTok{1e{-}3} \SpecialCharTok{*}\NormalTok{ C\_m }\SpecialCharTok{/}\NormalTok{ upars[[}\StringTok{"K\_c"}\NormalTok{]]) }\CommentTok{\# [1]}
\NormalTok{v\_cj }\OtherTok{=}\NormalTok{ j }\SpecialCharTok{/}\NormalTok{ (}\DecValTok{4} \SpecialCharTok{+} \DecValTok{4} \SpecialCharTok{*}\NormalTok{ phi) }\CommentTok{\# [1/s]}
\NormalTok{v\_cp }\OtherTok{=}\NormalTok{ k\_vc }\SpecialCharTok{*}\NormalTok{ upars[[}\StringTok{"R\_p"}\NormalTok{]] }\CommentTok{\# [1/s]}
\NormalTok{v\_cr }\OtherTok{=} \FunctionTok{apply}\NormalTok{(}\FunctionTok{cbind}\NormalTok{(v\_cj, v\_cp), }\DecValTok{1}\NormalTok{, min) }\CommentTok{\# [1/s]}
\NormalTok{v\_c }\OtherTok{=} \FunctionTok{apply}\NormalTok{(}\FunctionTok{cbind}\NormalTok{(k\_vc }\SpecialCharTok{*}\NormalTok{ upars[[}\StringTok{"E\_t"}\NormalTok{]], v\_cr), }\DecValTok{1}\NormalTok{, min) }\CommentTok{\# [1/s]}
\NormalTok{v\_o }\OtherTok{=}\NormalTok{ phi }\SpecialCharTok{*}\NormalTok{ v\_c }\CommentTok{\# [1/s]}
\NormalTok{A\_chl }\OtherTok{=}\NormalTok{ v\_c }\SpecialCharTok{{-}} \FloatTok{0.5} \SpecialCharTok{*}\NormalTok{ v\_o }\CommentTok{\# [1/s] \# i.e mol CO2 / mol Chl / s}
\NormalTok{A\_volume }\OtherTok{=}\NormalTok{ A\_chl }\SpecialCharTok{*}\NormalTok{ upars[[}\StringTok{"Q\_chl"}\NormalTok{]] }\CommentTok{\# [mol/m\^{}3/s]}
\end{Highlighting}
\end{Shaded}

To model photosynthesis and CO\(_2\) transport within a two-dimensional
cross section of the leaf, we built a grid of nodes of dimensions leaf
thickness by half the interstomatal distance. Nodes represent the leaf
mesophyll where CO\(_2\) diffusion and assimilation occur.

\textbf{Table X} Glossary of mathematical symbols. The columns indicate
the mathematical Symbol used in the paper, the associated symbol used in
R scripts, scientific Units, and a verbal Description.

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.1169}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.1039}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.3377}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.4416}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Symbol
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Value(s)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Units
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Description
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Biochemical Parameters & & & \\
\(A_\text{volume}\) & NA & \(mol CO_2/m^3/s\) & volumetric assimilation
rate \\
\(A_\text{chl}\) & NA & \(mol CO2/mol Chl/s\) & assimilation rate per
mol chlorophyll \\
\(E_t\) & 0.01 & \(mol / mol Chl\) & rubisco octamer concentration per
chlorophyll \\
\(eta_t\) & 0.59 & unitless & quantum efficiency of photoexcitation
transfer to reaction centers \\
\(k_c\) & 20 & \(mol CO2/mol Rubisco/s\) at 25 C & maximal carboxylation
velocity of Rubisco \\
\(k_o\) & 4.2 & \(mol O2/mol Rubisco/s\) at 25 C & maximal oxygenation
velocity of Rubisco \\
\(K_c\) & 0.0184 & \(mol/m^3\) at 25 C & Michaelis constant for CO2 \\
\(K_o\) & 13.2 & \(mol/m^3\) at 25 C & Michaelis constant for O2 \\
\(J_\text{max}\) & 0.253 & \(mol e\text{-}/mol Chl/s\) & maximal
electron transport rate per mol Chl \\
\(Q_\text{chl}\) & 3.3 & \(mol/m^3\) & Chl volume concentration \\
\(v_c\) & NA & \(mol CO2/mol Chl/s\) & carboxylation rate \\
\(v_o\) & NA & \(mol O2/mol Chl/s\) & oxygenation rate \\
\(k_\text{vc}\) & NA & \(mol CO2/mol Rubisco/mol Chl\) & carboxylation
velocity per Rubisco octamer at ambient CO2 \\
\(R_p\) & 0.273 & \(mol RuBP/mol Chl\) & RuBP pool size \\
\(k_i\) & 2.4 & \(1/m^2\) or \(1/L\) & light attenuation coefficient \\
\(D_\text{mc}\) & 7e-7 & \(m^2/s\) & diffusivity of CO\(_2\) in
mesophyll airspace \\
Environmental Parameters & & & \\
\(P\) & 101.325 & \(kPa\) & air pressure at sea level \\
\(temp\) & 298.15 & \(K\) & temperature \\
\(R_\text{gas}\) & 8.314 & \(J/K/mol\) & ideal gas constant \\
\(C_a\) & 16.96367 & \(mmol CO_2/m^3\) & atmospheric CO\(_2\)
concentration \\
\(O\) & 8.584027 & \(mol O_2/m^3\) & atmospheric \(O_2\)
concentration \\
\(PAR\) & 1000 & \(umol photons/m^2/s\) & photosynthetically active
radiation \\
Variables & & & \\
\(U_s\) & .05, .10, .15\ldots{} & \(mm\) & interstomatal distance \\
\(T_l\) & .1, .2, .3\ldots{} & \(mm\) & leaf thickness \\
\(g_\text{sc}\) & 0.2, 0.3, 0.4\ldots{} & \(mol/m^2/s\) & stomatal
conductance \\
\end{longtable}

\hypertarget{two-dimensional-model}{%
\subsection{Two-dimensional model}\label{two-dimensional-model}}

We used the \texttt{steady.2D()} function in the \emph{R} package
\textbf{rootSolve} version 1.8.2.4
(\protect\hyperlink{ref-soetaert_practical_2009}{\textbf{soetaert\_practical\_2009?}}).

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{diffusion2D }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{ (time, state, pars, stomata\_offset) \{}

\NormalTok{  n\_row }\OtherTok{=}\NormalTok{ pars[[}\StringTok{"n\_row"}\NormalTok{]]}
\NormalTok{  n\_col }\OtherTok{=}\NormalTok{ pars[[}\StringTok{"n\_col"}\NormalTok{]]}

\NormalTok{  n\_node }\OtherTok{=}\NormalTok{ n\_row }\SpecialCharTok{*}\NormalTok{ n\_col}

\NormalTok{  node\_length\_m }\OtherTok{=}\NormalTok{ node\_length }\SpecialCharTok{*} \FloatTok{1e{-}6} \CommentTok{\# node\_length in [m]}

  \CommentTok{\# matrix of C\_m values}
\NormalTok{  C\_m\_mat }\OtherTok{=} \FunctionTok{matrix}\NormalTok{(}\AttributeTok{nrow =}\NormalTok{ n\_row, }\AttributeTok{ncol =}\NormalTok{ n\_col, state)}

  \CommentTok{\# Photosynthetic demand}
  \DocumentationTok{\#\# Light matrix}
\NormalTok{  I\_mat }\OtherTok{=} \FunctionTok{seq}\NormalTok{(}\DecValTok{0}\NormalTok{, }\AttributeTok{by =}\NormalTok{ pars[[}\StringTok{"node\_length"}\NormalTok{]], }\AttributeTok{length.out =}\NormalTok{ n\_row) }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{light\_propogation}\NormalTok{(pars[[}\StringTok{"leaf\_thickness"}\NormalTok{]], pars[[}\StringTok{"PAR"}\NormalTok{]]) }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{matrix}\NormalTok{(n\_row, }\AttributeTok{ncol =}\NormalTok{ n\_col)}

  \DocumentationTok{\#\# Biochemical model}
  \CommentTok{\# Units have to be correct for this to work, but unitless = TRUE should be faster}
\NormalTok{  A }\OtherTok{=} \FunctionTok{biochemical\_model}\NormalTok{(C\_m\_mat, I\_mat, }\AttributeTok{pars =}\NormalTok{ pars, }\AttributeTok{unitless =} \ConstantTok{TRUE}\NormalTok{)}

  \DocumentationTok{\#\# Photosynthesis matrix}
  \DocumentationTok{\#\# multiply by 1000 to convert from mol / m\^{}3 / s to mmol / m\^{}3 / s}
\NormalTok{  A\_mat }\OtherTok{=} \FunctionTok{matrix}\NormalTok{(}\AttributeTok{nrow =}\NormalTok{ n\_row, }\AttributeTok{ncol =}\NormalTok{ n\_col, }\FloatTok{1e3} \SpecialCharTok{*}\NormalTok{ A)}

  \CommentTok{\# CO2 diffusion}
\NormalTok{  C\_a }\OtherTok{=} \FunctionTok{drop\_units}\NormalTok{(pars[[}\StringTok{"C\_a"}\NormalTok{]])}
\NormalTok{  flux\_mat }\OtherTok{=} \FunctionTok{matrix}\NormalTok{(}\AttributeTok{nrow =}\NormalTok{ n\_row, }\AttributeTok{ncol =}\NormalTok{ n\_col, }\DecValTok{0}\NormalTok{)}
\NormalTok{  flux\_mat[}\DecValTok{1}\NormalTok{, }\DecValTok{1}\NormalTok{] }\OtherTok{=}\NormalTok{ pars[[}\StringTok{"g\_sc"}\NormalTok{]] }\SpecialCharTok{*}\NormalTok{ (C\_a }\SpecialCharTok{{-}}\NormalTok{ C\_m\_mat[}\DecValTok{1}\NormalTok{, }\DecValTok{1}\NormalTok{])}

  \DocumentationTok{\#\# 1. Flux through stomata}
  \ControlFlowTok{if}\NormalTok{ (stomata\_offset) \{}
\NormalTok{    flux\_mat[n\_row, n\_col] }\OtherTok{=}\NormalTok{ pars[[}\StringTok{"g\_sc"}\NormalTok{]] }\SpecialCharTok{*}\NormalTok{ (C\_a }\SpecialCharTok{{-}}\NormalTok{ C\_m\_mat[n\_row, n\_col])}
\NormalTok{  \} }\ControlFlowTok{else}\NormalTok{ \{}
\NormalTok{    flux\_mat[n\_row, }\DecValTok{1}\NormalTok{] }\OtherTok{=}\NormalTok{ pars[[}\StringTok{"g\_sc"}\NormalTok{]] }\SpecialCharTok{*}\NormalTok{ (C\_a }\SpecialCharTok{{-}}\NormalTok{ C\_m\_mat[n\_row, }\DecValTok{1}\NormalTok{])}
\NormalTok{  \}}

\NormalTok{  zero\_x }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, n\_row)}
\NormalTok{  zero\_y }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, n\_col)}

  \DocumentationTok{\#\# 2. Mesophyll flux; zero fluxes near boundaries}
\NormalTok{  flux\_above }\OtherTok{=} \FunctionTok{rbind}\NormalTok{(}\FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, n\_col), C\_m\_mat[}\DecValTok{1}\SpecialCharTok{:}\NormalTok{(n\_row }\SpecialCharTok{{-}} \DecValTok{1}\NormalTok{), ] }\SpecialCharTok{{-}}\NormalTok{ C\_m\_mat[}\DecValTok{2}\SpecialCharTok{:}\NormalTok{n\_row, ])}
\NormalTok{  flux\_below }\OtherTok{=} \FunctionTok{rbind}\NormalTok{(C\_m\_mat[}\DecValTok{2}\SpecialCharTok{:}\NormalTok{n\_row, ] }\SpecialCharTok{{-}}\NormalTok{ C\_m\_mat[}\DecValTok{1}\SpecialCharTok{:}\NormalTok{(n\_row }\SpecialCharTok{{-}} \DecValTok{1}\NormalTok{), ], }\FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, n\_col))}
\NormalTok{  flux\_left  }\OtherTok{=} \FunctionTok{cbind}\NormalTok{(}\FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, n\_col), C\_m\_mat[, }\DecValTok{1}\SpecialCharTok{:}\NormalTok{(n\_col }\SpecialCharTok{{-}} \DecValTok{1}\NormalTok{)] }\SpecialCharTok{{-}}\NormalTok{ C\_m\_mat[, }\DecValTok{2}\SpecialCharTok{:}\NormalTok{n\_col])}
\NormalTok{  flux\_right }\OtherTok{=} \FunctionTok{cbind}\NormalTok{(C\_m\_mat[, }\DecValTok{2}\SpecialCharTok{:}\NormalTok{n\_col] }\SpecialCharTok{{-}}\NormalTok{ C\_m\_mat[, }\DecValTok{1}\SpecialCharTok{:}\NormalTok{(n\_col }\SpecialCharTok{{-}} \DecValTok{1}\NormalTok{)], }\FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{, n\_col))}

  \CommentTok{\# g\_mc [m/s] = D\_mc [m\^{}2/s] / node\_length [m]}
\NormalTok{  flux\_mat }\OtherTok{=}\NormalTok{ flux\_mat }\SpecialCharTok{+}\NormalTok{ pars[[}\StringTok{"g\_mc"}\NormalTok{]] }\SpecialCharTok{*}\NormalTok{ (flux\_above }\SpecialCharTok{+}\NormalTok{ flux\_below }\SpecialCharTok{+}\NormalTok{ flux\_left }\SpecialCharTok{+}\NormalTok{ flux\_right)}

    \FunctionTok{return}\NormalTok{(}\FunctionTok{list}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\FunctionTok{as.vector}\NormalTok{(flux\_mat }\SpecialCharTok{/}\NormalTok{ node\_length\_m }\SpecialCharTok{{-}}\NormalTok{ A\_mat))))}

\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

\hypertarget{global-results}{%
\subsection{Global Results}\label{global-results}}

@@

>>>>

@@

@@

\usepackage[nomarkers,tablesfirst]{endfloat}
\usepackage{lineno}
\linenumbers
\usepackage{hyperref}
\renewcommand{\figureautorefname}{Fig.}
\usepackage{booktabs}

@@

We modeled photosynthesis CO\(_2\) assimilation rate using a
spatially-explicit two-dimensional reaction diffusion model using a
porous medium approximation
(\protect\hyperlink{ref-parkhurst_intercellular_1994}{\textbf{parkhurst\_intercellular\_1994?}})
using the finite element method (FEM) following
(\protect\hyperlink{ref-earles_excess_2017}{\textbf{earles\_excess\_2017?}}).
Consider a two-dimensional leaf where stomata occur on each surface in a
regular sequence with interstomatal distance \(U\). The main outcome we
assessed is the advantage of offsetting the position of stomata on each
surface compared to have stomata on the same \(x\) position on each
surface. With these assumptions, by symmetry, we only need to model two
stomata, one abaxial and one adaxial, from \(x = 0\) to \(x = U/2\) and
from the adaxial surface at \(y = 0\) to the abaxial surface at
\(y = L\), the leaf thickness. We arbitrarily set the adaxial stomate at
\(x = 0\) and toggled the abaxial stomata position between \(x = U/2\)
(offset) or \(x = 0\) (below adaxial stomate). The `coordination
advantage' of offset stomatal position on each surface is the
photosynthetic rate of the leaf with offset stomata compared to that
with stomata aligned in the same \(x\) position:

@@

@@

\hypertarget{results-1}{%
\section{Results}\label{results-1}}
